---
title: "Scenario Indices - examples"
author: "Christiana Photiaodu & Martin Roth"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{potentialEvaporation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r LoadLibraries, include=FALSE}
library(data.table)
library(scenarioIndices)
library(knmitransformer)
```

The *scenarioIndices* package calculates a set of indices that were published in the KNMI'14 Climate scenarios and uses the *knmitransformer* package for the transformed series. This document provides examples on how to use the function to calculate evaporation, precipitation and temperature indices in different seasonal periods. 

## Potential Evaporation Makkink

For the KNMI'14 Climate Scenarios brochure the annual and summer potential evaporation sum is presented.
```{r makkinkevaporation}
inputTemp <- KnmiRefFile("KNMI14____ref_tg___19810101-20101231_v3.2.txt")
inputRad  <- KnmiRefFile("KNMI14____ref_rsds___19810101-20101231_v3.2.txt")
ofile     <- "tmp.txt" # output file - used only temporary
var <- "tg"
regions <- MatchRegionsOnStationId(ReadInput(var, inputTemp)$header[1, -1])
  scenario = "GL"

  horizon = 2030

  tmp <- evmkSumsRelchange(inputTemp=inputTemp, inputRad=inputRad,
                             ofile = ofile,
                             scenario = scenario,
                             horizon = horizon,
                             regions = regions)
```
## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
