---
title: "Scenario Indices - examples"
author: "Christiana Photiaodu & Martin Roth"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{potentialEvaporation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r LoadLibraries, include=FALSE}
library(data.table)
library(scenarioIndices)
library(knmitransformer)
library(futile.logger)
flog.threshold(ERROR)
```

The *scenarioIndices* package calculates a set of indices that were published in the KNMI'14 Climate scenarios and uses the *knmitransformer* package for the transformed series. This document provides examples on how to use the function to calculate evaporation, precipitation and temperature indices in different seasonal periods. 

## Potential Evaporation Makkink

In the KNMI'14 Climate Scenarios brochure the annual and summer potential evaporation sum is presented. For this, the following need to be specified; temperature and radiation data sets, scenario and horizon.
```{r makkinkevaporation}
inputTemp <- KnmiRefFile("KNMI14____ref_tg___19810101-20101231_v3.2.txt")
inputRad  <- KnmiRefFile("KNMI14____ref_rsds___19810101-20101231_v3.2.txt")
regions <- MatchRegionsOnStationId(ReadInput("tg", inputTemp)$header[1, -1])
scenario = "GL"  
horizon = 2030
```

```{r evmksums}
  EvapRelChange <- evmkSumsRelchange(inputTemp=inputTemp, inputRad=inputRad,
                             scenario = scenario,
                             horizon = horizon,
                             regions = regions)
  
  EvapRelChange
```
The above table shows the relative change between the evaporation sums for GL 2030 and the reference data/period(1981-2010) for each station (columns) for the the annual change and the 4 seasons, winter, spring, summer, and autumn(rows.) 

## Precipitation Deficit
To calculate the index for precipitation deficit we must first specify the three input data sets for temperature, radiation and precipitation, and of course the regions for the temprature stations (knmitransformer)
```{r neerslagtekort}

inputTemp <- KnmiRefFile("KNMI14____ref_tg___19810101-20101231_v3.2.txt")
inputRad  <- KnmiRefFile("KNMI14____ref_rsds___19810101-20101231_v3.2.txt")
inputPrec <- KnmiRefFile("KNMI14____ref_rrcentr___19810101-20101231_v3.2.txt")
regions   <- MatchRegionsOnStationId(ReadInput("tg", inputTemp)$header[1, -1])
```
Then specify the scenario and horizon we would like to calculate the index:
```{r neerslagtekort2}
  scenario = "WL"
  horizon = 2050

  precdefic <- PrecipDeficit(inputTemp = inputTemp, inputRad = inputRad,
                           inputPrec = inputPrec, scenario = scenario,
                           horizon = horizon,
                           regions = regions)
```

```{r neerslagtekort3}
head(precdefic)
```
The second column (WL2050) 
## Precipitation threshold indices
A set of precipitation threshold indices can be calculated using the following function
```{r precipindices}
 input <- KnmiRefFile("KNMI14____ref_rrcentr___19810101-20101231_v3.2.txt")
 input <- ReadInput("rr", input)
 PrecIndicesRef <- PrecIndicesWrapper(input$obs)
```
```{r showprecindices}
 head(PrecIndicesRef)
```
This table shows the calculate indices with thresholds: 0.1, 0.5, 10, 20, and 30 mm, for all seasons (year, & 4 seasons) for 104 precipitation stations.

## Temperature indices
* Indices calculated regarding daily average temperature
The following specifications are required:
```{r tgindices}
 input   <- KnmiRefFile("KNMI14____ref_tg___19810101-20101231_v3.2.txt")
 regions <- MatchRegionsOnStationId(ReadInput("tg", input)$header[1, -1])
```
Using the following wrapper function we can get a table with all related indices for all horizons and scenarios (including reference period) for all 4 seasons and annual values, for all temperature stations.
```{r tgindicesshow}
  tgindices <- TempAvgIndicesWrapper(input, regions = regions)

```

```{r tgindiesagain}
head(tgindices)
```

* Indices calculated using daily maximum temperature

Similar to the previous indices:
```{r txindices}
input   <- KnmiRefFile("KNMI14____ref_tx___19810101-20101231_v3.2.txt")
regions <- MatchRegionsOnStationId(ReadInput("tx", input)$header[1, -1])
```

```{r txindicesagain}
  txindices <- TempMaxIndicesWrapper(input, regions = regions)
```

```{r txindicesshow}
head(txindices)
```

* Indices calculated using daily minimum temperature

Similar to the previous indices:
```{r tnindices}
input   <- KnmiRefFile("KNMI14____ref_tn___19810101-20101231_v3.2.txt")
regions <- MatchRegionsOnStationId(ReadInput("tn", input)$header[1, -1])
```

```{r tnindicesagain}
  tnindices <- TempMinIndicesWrapper(input, regions = regions)
```

```{r tnindicesshow}
head(tnindices)
```
